### 2019-03-24 Sections/how_to_learn_more.tex
minor

\dropcap{F}{or} the reader interested in delving deeper into quantum technology with a hands-on approach, there are a number of freely available software tools for simulating various quantum technologies, including quantum computing and quantum networks. We summarise some of the major ones below, all of which are freely available:

\begin{itemize}
	\item SimulaQron\index{SimulaQron} (\href{http://www.simulaqron.org}{http://www.simulaqron.org}): Developed by QuTech Delft \cite{bib:AxelDahlbergQron}, a simulator for designing software for the quantum internet. The package includes its own quantum internet programming language for deploying networked quantum algorithms. The institute runs competitions for designing the best quantum internet app.
	\item Google Cirq\index{Cirq} (\href{https://github.com/quantumlib/Cirq}{https://github.com/quantumlib/Cirq}): Google's Python-based SDK for designing quantum software, specifically targeted at development for Google's own in-house quantum computing hardware platform.
	\item Microsoft Quantum Development Kit and the Q\# language\index{Q\#}\index{Microsoft Quantum Development Kit} (\href{https://www.microsoft.com/en-au/quantum/development-kit}{https://www.microsoft.com/en-au/quantum/development-kit}): a full SDK for writing code executable on quantum computers. The Q\# language is used to describe quantum operations, which classical code written in C\#\index{C\#} can interface with and control. The platform is extremely versatile and allows highly complex quantum operations to be coded in a high-level, platform-independent manner. The platform includes a simulator for executing code for which the hardware doesn't yet exist.
	\item IBM Quantum Experience\index{IBM!Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}): IBM's cloud-based platform for remotely executing simple quantum protocols, as written and uploaded to the cloud by the user. The platform includes QISKit, a Python-based SDK for executing quantum algorithms. It is based on the Open Quantum Assembly Language (OpenQASM) language\index{OpenQASM}.
	\item Rigetti Quantum Cloud Services (QCS)\index{Rigetti Quantum Cloud Services} (\href{https://www.rigetti.com/qcs}{https://www.rigetti.com/qcs}): Rigetti's cloud platform for accessing and deploying algorithms to their hardware over the cloud. Development is powered by the Forest SDK\index{Forest SDK}, their own in-house development platform.
	\item Keep looking, as the list is rapidly growing with new participants entering the market regularly\ldots
\end{itemize}

>>>>

\dropcap{F}{or} the reader interested in delving deeper into quantum technology with a hands-on approach, there are a number of freely available software tools for simulating various quantum technologies, including quantum computing and quantum networks. We highlight some of the major ones below, all of which are freely available:

\begin{itemize}
	\item SimulaQron\index{SimulaQron} (\href{http://www.simulaqron.org}{http://www.simulaqron.org}): Developed by QuTech Delft \cite{bib:AxelDahlbergQron}, a simulator for designing software for the quantum internet. The package includes its own quantum internet programming language for deploying networked quantum algorithms. The institute runs competitions for designing the best quantum internet app.
	\item Google Cirq\index{Cirq} (\href{https://github.com/quantumlib/Cirq}{https://github.com/quantumlib/Cirq}): Google's Python-based SDK for designing quantum software, specifically targeted at development for Google's own in-house quantum computing hardware platform.
	\item Microsoft Quantum Development Kit and the Q\# language\index{Q\#}\index{Microsoft Quantum Development Kit} (\href{https://www.microsoft.com/en-au/quantum/development-kit}{https://www.microsoft.com/en-au/quantum/development-kit}): a full SDK for writing code executable on quantum computers. The Q\# language is used to describe quantum operations, which classical code written in C\#\index{C\#} can interface with and control. The platform is extremely versatile and allows highly complex quantum operations to be coded in a high-level, platform-independent manner. The platform includes a simulator for executing code for which the hardware doesn't yet exist.
	\item IBM Quantum Experience\index{IBM!Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}): IBM's cloud-based platform for remotely executing simple quantum protocols, as written and uploaded to the cloud by the user. The platform includes QISKit\index{QISKit} (\href{https://qiskit.org}{https://qiskit.org}), a Python-based SDK for executing quantum algorithms. It is based on the Open Quantum Assembly Language (OpenQASM) language\index{OpenQASM}.
	\item Rigetti Quantum Cloud Services (QCS)\index{Rigetti Quantum Cloud Services} (\href{https://www.rigetti.com/qcs}{https://www.rigetti.com/qcs}): Rigetti's cloud platform for accessing and deploying algorithms to their hardware over the cloud. Development is powered by the Forest SDK\index{Forest SDK}, their own in-house development platform.
	\item Keep looking, as the list is rapidly growing with new participants entering the market regularly\ldots
\end{itemize}

### 2019-03-24 Sections/optimising_the_world.tex
minor

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{graph_colouring}\\
\includegraphics[clip=true, width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graphs!Colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{graph_colouring}\\
\includegraphics[clip=true, width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\footnote{\famousquote{I say to you that you are better than a Frenchman. I would lay even money that you who are reading this are more than five feet seven in height, and weigh eleven stone; while a Frenchman is five feet four and does not weigh nine. The Frenchman has after his soup a dish of vegetables, where you have one of meat. You are a different and superior animal -- a French-beating animal (the history of hundreds of years has shown you to be so).}{William Thackeray}}\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'\index{Four colour theorem}.}\index{Graphs!Colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}
